Verifying Spatial Properties of Stencil Computations

### 2016-11-16 paper.tex
section names and bib plain and some edits

\documentclass[10pt,preprint]{sigplanconf}

@@

\usepackage{tikz}
\usepackage{xypic}
\usepackage{natbib}

@@

\usepackage{cleveref}
\crefname{section}{\S}{\S\S}
\Crefname{section}{\S}{\S\S}
\crefname{subsection}{\S\S}{\S\S\S}
\Crefname{subsection}{\S\S}{\S\S\S}
\crefname{figure}{fig.}{}
\Crefname{figure}{Fig.}{}
\crefname{definition}{def.}{}
\Crefname{definition}{Def.}{}

@@

\bibliographystyle{abbrvnat}

@@

\begin{definition}
A \emph{zeroed single-entry vector} of size $n$, denoted
$\zeroEntry{r}{n}$, is a vector where the $r^{th}$ entry is $0$ and all others
are $\infty$, \eg{}, $\zeroEntry{1}{2} = \vtwoh{0}{\infty}$.
Similarly to single-entry vectors, zeroed single-entry vectors
generalise all other schemes
that have $0$ as their $r^{th}$, representing indices at
the ``origin'' in dimension $r$.
\end{definition}

@@

Specifications have a theory of equality, $\equiv$, providing axiomatic
semantics for the language. This enables users to rewrite their specification
and helps the inference procedure (\Cref{subsec:inference}) simplify
specifications. Additionally, specifications have a theory of approximation,
$<:$, that can be used by the users to weaken specifications for succintness in
the source.

>>>>

\documentclass[10pt,preprint,numbers]{sigplanconf}

@@

\usepackage{tikz}
\usepackage{xypic}
%\usepackage{natbib}

@@

\usepackage{cleveref}
\crefname{section}{\S}{\S\S}
\Crefname{section}{\S}{\S\S}
\crefname{subsection}{\S}{\S\S\S}
\Crefname{subsection}{\S}{\S\S\S}
\crefname{figure}{fig.}{}
\Crefname{figure}{Fig.}{}
\crefname{definition}{def.}{}
\Crefname{definition}{Def.}{}

@@

\bibliographystyle{plain}

@@

\begin{definition}
A \emph{zeroed single-entry vector} of size $n$ denoted
$\zeroEntry{r}{n}$ is a vector where the $r^{th}$ entry is $0$ and all others
are $\infty$ \eg{}, $\zeroEntry{1}{2} = \vtwoh{0}{\infty}$.
Akin to single-entry vectors, zeroed single-entry vectors
generalise all other schemes
that have $0$ as their $r^{th}$ entry, representing indices at
the ``origin'' in $r$.
\end{definition}

@@

Specifications have a theory of equality, $\equiv$, providing axiomatic
semantics for the language. This enables users to rewrite their specification
and provides a way to automatically simplify
specifications after inference (\Cref{subsec:inference}).
Additionally, specifications have a theory of approximation,
$<:$, that can be used by the users to weaken specifications for succintness in
the source.
